Weakly Nonlinear MRI: Notes

### 2014-10-16 notes/mri_notes.tex
more paper and minor notes clarification
notes typo
nondimensionalization, thin gap
started adding hMRI notes

And we introduce the following terms:
\[\reye \equiv \frac{\Omega_0 r_0^2 \delta^2}{\nu} ; \, \, \, \reym \equiv \frac{\Omega_0 r_0^2 \delta^2}{\eta}\]

@@

$-\epsilon^2\partial_z\mathcal{X} \to \left(-\epsilon^2 - \epsilon^3\partial_Z\right)\mathcal{X}$ \\

@@

We drop the $\partial_t$ terms and our $\mathcal{O}(\epsilon^2)$ equation is: \\

@@

>>>>

And we introduce the following terms:
\[\reye \equiv \frac{\Omega_0 r_0^2 \delta^2}{\nu} \reym \equiv \frac{\Omega_0 r_0^2 \delta^2}{\eta}\]

@@

$-\epsilon^2\partial_z\mathcal{X} \to \left(-\epsilon^2\partial_z - \epsilon^3\partial_Z\right)\mathcal{X}$ \\

@@

We drop the $\partial_t$ terms and our equation up to order $\mathcal{O}(\epsilon^2)$ is: \\

@@

\pagebreak
\section*{Helical MRI}

Instead of the standard MRI, we initialize an azimuthal field in addition to the constant vertical field. The azimuthal field will linearly decrease radially, since in any reasonable setup it will be created by an axial current through the center of the apparatus.

The base state becomes:

\begin{equation}
\mathbf{B} = B_0 \hat{z} + \xi B_0 \left(\frac{x_1}{x}\right) \hat{y} + \mathbf{B}_1
\end{equation}
